Towards Bringing Together Numerical Methods for Partial Differential Equation and Image Processing

### 2020-03-30 paper/eccv2020submission.tex
Small fixes

      Constant           &14.56(1.97)&44.04(18.73)&0.60(0.29)&0.72(0.54)  \\
      Inflow speed       &32.16(0.55)&45.68(1.21)&0.55(0.05)&0.93(0.07)   \\
      Viscosity-density  &57.00(42.46)&14.70(2.65)&13.85(13.43)&0.37(0.09)\\
    \end{tabular}
  \end{center}
  \caption{All of the given numbers are in percent. In the brackets we also give the standard deviation of the corresponding metric. }\label{tab:single}
\end{table}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{l|cc|cc}
      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation 8}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation 39}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
      \hline 
                     &\multicolumn{2}{c|}{} & &\\
                     & {Average difference} & {Max difference}  &  {Max difference} & {Average difference}\\
      \emph{Frame 1}       &34.27(0.02) & 52.72(0.40)    &35.91(0.02) & 51.76(0.38)   \\
      \emph{Frame 5}       &33.86(0.11) & 60.41(1.62)    &35.84(0.10) & 53.13(0.54)   \\
      \emph{Frame 10}      &33.99(0.17) & 66.04(2.16)    &36.01(0.15) & 54.59(1.14)   \\
      \emph{Frame 15}      &33.80(0.20) & 76.40(3.67)    &35.91(0.20) & 58.90(1.97)   \\
      \emph{Frame 20}      &34.27(0.22) & 75.39(3.07)    &35.89(0.24) & 62.60(2.94)   \\
      \emph{Frame 25}      &33.91(0.22) & 83.45(3.06)    &35.93(0.28) & 61.07(2.60)   \\
      \emph{Frame 30}      &34.13(0.24) & 79.15(2.20)    &35.73(0.33) & 66.69(4.21)   \\
      \emph{Frame 35}      &34.38(0.23) & 83.52(2.09)    &35.94(0.35) & 65.55(4.18)   \\      
    \end{tabular}
  \end{center}
  \caption{}\label{tab:recursive_inflow}
\end{table}

\begin{table}
  \begin{center}
    \begin{tabular}{l|cc|cc}
      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation 8}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation 39}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
      \hline 
                     &\multicolumn{2}{c|}{} & &\\
                     & {Average difference} & {Max difference}  &  {Max difference} & {Average difference}\\
      \emph{Frame 1}       &35.87(0.03) & 52.04(0.38)           &35.27(0.00) & 52.16(1.45)   \\
      \emph{Frame 5}       &36.33(0.16) & 54.48(0.89)           &35.27(0.02) & 54.23(3.28)   \\
      \emph{Frame 10}      &35.75(0.24) & 55.87(1.57)           &35.28(0.04) & 54.89(3.31)   \\
      \emph{Frame 15}      &35.77(0.30) & 58.47(2.10)           &35.29(0.06) & 55.67(2.79)   \\
      \emph{Frame 20}      &35.66(0.32) & 59.87(2.54)           &35.30(0.09) & 56.59(2.05)   \\
      \emph{Frame 25}      &35.63(0.37) & 60.86(2.54)           &35.32(0.11) & 57.54(2.48)   \\
      \emph{Frame 30}      &35.64(0.40) & 61.16(3.37)           &35.34(0.13) & 58.30(3.05)   \\
      \emph{Frame 35}      &35.78(0.39) & 63.11(1.57)           &35.36(0.15) & 59.17(3.42)   \\      
    \end{tabular}
  \end{center}
  \caption{Your caption.}\label{tab:recursive_fluid}
\end{table}

>>>>

      Constant           &14.56(1.97)&44.04(18.73)&0.60(0.29)&0.72(0.54)  \\
      Inflow speed       &32.16(0.55)&45.68(1.21)&0.55(0.05)&0.93(0.07)   \\
      Viscosity-density  &57.00(42.46)&14.70(2.65)&13.85(13.43)&0.37(0.09)\\
    \end{tabular}
  \end{center}
  \caption{All of the given numbers are in percent. In the parenthesis we also give the standard deviation of the corresponding metric. }\label{tab:single}
\end{table}

@@

\begin{table}
  \begin{center}
    Inflow speed model
  \end{center}
  \begin{center}
    \begin{tabular}{l|cc|cc}
     \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Start index: 120}\\$g=1.9487$}}& \multicolumn{2}{c}{\shortstack{\textbf{Start index: 120}\\$g=3.9358$}}\\
      \hline 
                     &\multicolumn{2}{c|}{} & &\\
                     & {Average difference} & {Max difference}  &  {Average difference} & {Max difference}\\
      \emph{Frame 1}       &34.27(0.02) & 52.72(0.40)    &35.91(0.02) & 51.76(0.38)   \\
      \emph{Frame 5}       &33.86(0.11) & 60.41(1.62)    &35.84(0.10) & 53.13(0.54)   \\
      \emph{Frame 10}      &33.99(0.17) & 66.04(2.16)    &36.01(0.15) & 54.59(1.14)   \\
      \emph{Frame 15}      &33.80(0.20) & 76.40(3.67)    &35.91(0.20) & 58.90(1.97)   \\
      \emph{Frame 20}      &34.27(0.22) & 75.39(3.07)    &35.89(0.24) & 62.60(2.94)   \\
      \emph{Frame 25}      &33.91(0.22) & 83.45(3.06)    &35.93(0.28) & 61.07(2.60)   \\
      \emph{Frame 30}      &34.13(0.24) & 79.15(2.20)    &35.73(0.33) & 66.69(4.21)   \\
      \emph{Frame 35}      &34.38(0.23) & 83.52(2.09)    &35.94(0.35) & 65.55(4.18)   \\      
    \end{tabular}
  \end{center}
  \caption{Again, all of the numbers are in percents and are averaged across the evaluations of models trained only with difference in the used seed. The standard deviation is given in the parenthesis. To note is that the maximum difference is high for almost all frames. This is to be expected from our models as they primarily target the visual quality of the results. The average difference on the other hand stays relatively stable across the frames. Still, average difference of over 30\% unsatisfactory even for course simulation.}\label{tab:recursive_inflow}
\end{table}

\begin{table}
  \begin{center}
    Viscosity-density model
  \end{center}
  \begin{center}
    \begin{tabular}{l|cc|cc}
      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Start index: 120}\\$\rho=4.1764, \nu=0.001023$}}&\multicolumn{2}{c}{\shortstack{\textbf{Start index: 120}\\$\rho=6.8235, \nu=0.002876$}}\\
      \hline 
                     &\multicolumn{2}{c|}{} & &\\
                     & {Average difference} & {Max difference}  &  {Average difference} & {Max difference}\\
      \emph{Frame 1}       &35.87(0.03) & 52.04(0.38)           &35.27(0.00) & 52.16(1.45)   \\
      \emph{Frame 5}       &36.33(0.16) & 54.48(0.89)           &35.27(0.02) & 54.23(3.28)   \\
      \emph{Frame 10}      &35.75(0.24) & 55.87(1.57)           &35.28(0.04) & 54.89(3.31)   \\
      \emph{Frame 15}      &35.77(0.30) & 58.47(2.10)           &35.29(0.06) & 55.67(2.79)   \\
      \emph{Frame 20}      &35.66(0.32) & 59.87(2.54)           &35.30(0.09) & 56.59(2.05)   \\
      \emph{Frame 25}      &35.63(0.37) & 60.86(2.54)           &35.32(0.11) & 57.54(2.48)   \\
      \emph{Frame 30}      &35.64(0.40) & 61.16(3.37)           &35.34(0.13) & 58.30(3.05)   \\
      \emph{Frame 35}      &35.78(0.39) & 63.11(1.57)           &35.36(0.15) & 59.17(3.42)   \\      
    \end{tabular}
  \end{center}
  \caption{For the viscosity-density model the average differences are again stable across the frames of the predicted simulations. The maximum differences grow as the predictions get more inaccurate and more artefacts appear in the predicted frames.}\label{tab:recursive_fluid}
\end{table}
